\documentclass{article}
\usepackage{bookmark}
\usepackage{calc}
\usepackage[top=0.4in,bottom=0.3in,right=0.5in,left=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{tgbonum}
\usepackage{fontawesome}

\setlist[enumerate]{topsep=0pt}
\setlist[itemize]{noitemsep,topsep=0pt}

\newlength{\remaining}
\renewcommand{\section}[1]{
  \vspace{1.0em}\setlength{\remaining}{\textwidth-\widthof{\uppercase{#1}}}
    \noindent\underline{\fontsize{10}{15}\bfseries\uppercase{#1}\hspace*{\remaining}} \\
}

\renewcommand{\subsection}[3]{
    \noindent\textbf{#1} | \emph{#2} \hfill #3  
}

\begin{document}
    \fontencoding{T1}
    \fontfamily{phv}
    \fontsize{11}{16}
    \selectfont

    \begin{center}
        \Huge\bfseries Hakancan Ozturk
    \end{center}
    
    \begin{center}
        \begin{tabular}{c c c c c}
            \href{mailto:hakancan.ozturk23@gmail.com}{\small hakancan.ozturk23@gmail.com  } $\bullet$ & 
            \href{tel:+44 7436010077}{\small +44 7436010077  } $\bullet$ & 
            \href{https://www.linkedin.com/in/hakancan}{\small \faLinkedinSquare \space linkedin/hakancan} $\bullet$ & 
            \href{https://www.github.com/hkc5} {\small \faGithub \space github/hkc5 } $\bullet$ &  
            \href{https://www.hakancanozturk.com}{\small hakancanozturk.com} \\
        \end{tabular}   
    \end{center}
    
    \vspace{-0.75em}
    
    \section{Professional Experience}
    \subsection{Software Development Engineer}{\textbf{Amazon} - London, UK}{01/2025 - Present}
    \begin{itemize}
        \item Optimizing Prime Video UI components, reducing rendering time by 10\% for over 100M customers, improving app responsiveness on low-end devices through LLM-powered automation pipelines.
        \item Investigated and found inefficiencies in the Prime Video TV app, optimizing the code to use 4\% less memory for over 200M customers, improving performance on resource-constrained devices.
        \item Developed LLM agent platform for real-time analysis of 10M+ Prime Video operational metrics, enabling rapid system regression detection and award recognition at London-wide Amazon hackathon.
        \item Supervised 3-month internship extending AI agent capabilities for oncall investigation, now productionizing the platform for 100+ engineers.
    \end{itemize}

    \subsection{Founding Engineer}{\textbf{Albus Technologies} - London, UK}{05/2024 - 01/2025}
    \begin{itemize}
        \item Engineered and optimized a scalable Retrieval-Augmented Generation (RAG) system with context-enriched vector search, boosting retrieval relevance by 30\% and serving 50K+ users.
        \item Developed scalable real-time Document Semantic Extraction pipelines and LLM agents using AWS (Lambda, S3, SQS, EC2), processing millions of PDF pages and over hundreds of hours of audio.
        \item Established automated CI/CD workflows (Docker, GitHub Actions) to deploy FastAPI and Lambda endpoints, enabling dozens of concurrent file uploads with low-latency, robust production.
    \end{itemize}
    

    \subsection{Computing Researcher}{\textbf{Max Planck Institute} - Stuttgart, Germany}{06/2022 - 12/2022}
    \begin{itemize}
        \item Enhanced robotics dynamics prediction by deploying ML data pipelines analyzing 10TB simulation data; optimized CFD simulations via novel HPC scheduling, achieving 200x speedup, enabling 4 publications.
    \end{itemize}

    
    \section{Education}
    \subsection{Imperial College London}{MSc in Applied Computational Science and Engineering}{2023-2024} \\
    Highest overall grade in class | Class representative  \hfill Distinction (78.27\%) \\
    \textit{Modules:} Machine/Deep Learning, Numerical Methods, Computational Maths, Optimization
    
    \vspace{0.25em}

    \subsection{Koc University}{BSc in Mechanical Engineering}{2020-2023} \\
    Ranked 1st in class | Graduated one year early | Merit scholarship (\$30k annually) \hfill GPA: 3.99/4.00

    \vspace{0.25em}

    \subsection{Robert College}{High School Diploma}{2015-2020} \\
    AP Chemistry: 5/5 | AP Calculus AB: 5/5 | IELTS: 8.0/9.0

    \section{Projects}
    \subsection{AI Surrogate Modeling for Turbulent Flow Simulations}{Imperial College London}{2024 - 2025} 
    \begin{itemize} 
        \item Discovered a novel Grid-Invariant AI architecture (PyTorch) combining convolutional autoencoders and adversarial networks to simulate high-fidelity turbulent flows, achieving unprecedented grid independence and scalability.
        \item Conducted 2000+ GPU hours of High-Performance Computing (HPC) for model optimization, enhancing long-term stability by 35\% and prediction accuracy by 50\%.
        \item Actively open-sourcing advancements (manuscripts in prep/review), with project development backed by big tech companies and university institutions.
    \end{itemize}

    \subsection{Advanced Collagen Fiber Orientation Analysis}{Pekkan Biofluid Mechanics Laboratory}{2023 – 2024}
    \begin{itemize}
        \item Directed advanced bio-imaging analysis (FFT, SVR, CNNs) achieving 95\% accuracy in collagen orientation prediction, while also implementing novel Generative Diffusion Models (PyTorch) for 10x biological data augmentation.
    \end{itemize}

    \subsection{Earthquake Predictive Modeling}{Graduation Project - Koc University}{2023}
    \begin{itemize}
        \item Developed predictive modeling framework for earthquake impact assessment in Turkey, focusing on viscous wall dampers performance optimization using computational mechanics and ML techniques, ranked 2nd in university.
    \end{itemize}

    \subsection{TUSAS Aerospace Industry Collaboration}{ML Failure Prediction Models}{2021}
    \begin{itemize}
        \item Built ML prediction models for failure detection in aerospace components in collaboration with Turkish Aerospace Industries (TUSAS), awarded 2nd place in annual university-industry partnership program.
    \end{itemize}


\section{Leadership \& Mentoring}
\subsection{Amazon Software Engineering Intern Mentorship}{Prime Video Team}{2025}
\begin{itemize}
    \item Mentored software engineering intern over 3-month period, co-developing project deliverables and securing return offer through successful performance guidance.
\end{itemize}

\subsection{Imperial College Students Mentoring}{Amazon University Engagement Program}{2025}
\begin{itemize}
    \item Leading 3 Imperial College students on Revizion, an AI-powered GCSE and A-levels review app development through Amazon University Engagement Program.
    \item Guiding technical stack selection, system design, AI features implementation, and software engineering best practices while leading the end-to-end project development.
\end{itemize}

\subsection{Koc University Students Mentoring}{AI/ML Projects}{2025}
\begin{itemize}
    \item Mentoring 2 Koc University students in AI/ML projects, helping them build applications with industry-standard software engineering practices and providing technical guidance on system architecture.
\end{itemize}

\section{Speaking \& Media Coverage}
\subsection{Amazon Engineering Presentation}{Agentic AI Tools and MCPs}{2025}
\begin{itemize}
    \item Presented "Agentic AI Tools and MCPs for Engineering Tasks" to 30+ Amazon engineers in person, with 500+ Amazon engineers viewing online and 1000+ engineers viewing the setup video.
\end{itemize}

\subsection{Koc University Mechanical Engineering Society Podcast}{Studies and Careers in UK}{2024}
\begin{itemize}
    \item Discussed studies and careers in the UK (English) - 500+ YouTube views.
\end{itemize}

    \section{Skills}
    Languages: Python, TypeScript/JavaScript, C++, MATLAB \\
Libraries \& Frameworks: PyTorch, scikit-learn, pandas, numpy, FastAPI, React, LangChain \\
Cloud \& DevOps: Docker, AWS, Github Actions, Terraform, HPC, Parallel Computing
% \textbf{Engineering Software}: COMSOL (CFD), ANSYS (Mechanics, Fluent), Siemens NX

\section{Achievements \& Awards}
\vspace{-1.25em}
\begin{itemize}
    \item Koc University Early Graduation: First student in university history to complete 4-year Mechanical Engineering degree in 3 years while ranking 1st in class.
    \item Y Combinator AI Startup School (San Francisco, 2025): Selected among top 2000 CS students/grads globally, networked with YC partners and received invitation to apply to YC batch.
    \item Viridien \& Imperial College Hackathon Winner (1st out of 30 teams): Developed classification ML models for Carbon Capture \& Seismic Data Analysis.
    \item Turkish University Entrance Exam: Ranked 300th out of 2 million students nationwide (top 0.015\%)
    \item Turkish High School Entrance Exam: Ranked 1st out of 1 million students nationwide
    \item KPMG Ideation Challenge National Winner and global finalist: Co-developed an AI-driven mental wellness application.
    % \item AP Scores: Chemistry (5/5), Calculus (5/5).
    \end{itemize}

\newpage

\section{Publications}
\noindent\textit{5 papers, 27+ citations}
\vspace{0.75em}

Ozturk, H.*, Bozuyuk, U.*, \& Sitti, M. (2023). Microrobotic locomotion in blood vessels: a computational study on the performance of surface microrollers in the cardiovascular system. \textit{Advanced Intelligent Systems}, 5(9), 2300099.

\vspace{0.5em}

Bozuyuk, U.*, Ozturk, H.*, \& Sitti, M. (2023). The mismatch between experimental and computational fluid dynamics analyses for magnetic surface microrollers. \textit{Scientific Reports}, 13, 10196.

\vspace{0.5em}

Saruhan, E. N., Ozturk, H., Kul, D., Sevgin, B., Coban, M. N., \& Pekkan, K. (2025). Learning-enhanced 3D fiber orientation mapping in thick cardiac tissues. \textit{Biomedical Optics Express}, 16(8), 3315-3336.

\vspace{0.5em}

Arslan, B., Bozuyuk, U., Görgülü, K., Yildiz, E., Ozturk, H., Liotta, L., Heinemann, V., Algül, H., \& Sitti, M. (2025). Anisotropic Surface Microrollers for Endovascular Navigation: A Computational Analysis with a Case Study in Hepatic Perfusion. \textit{Advanced Theory and Simulations}, 2400387.

\vspace{0.5em}

Yorulmaz, M., Bozuyuk, U., Park, M., Arslan, B., Ozturk, H., Aghakhani, A., \& Sitti, M. (2025). Locomotion Behavior of Magnetic Microrollers in Confined Tubular Geometries Containing Shear-Thinning Fluids. \textit{MARSS 2025}, West Lafayette, USA.

\end{document}
